\begin{frame}{replay attacks}
    \begin{itemize}
    \item A$\rightarrow$B: Did you order lunch? [signature 1 by A]
        \begin{itemize}
            \item signature 1 by A = Sign(A's private signing key, ``Did you order lunch?'')
            \item check with Verify(A's public key, signature 1 by A, ``Did you order lunch?'')
        \end{itemize}
    \item B$\rightarrow$A: Yes. [signature 1 by B]
        \begin{itemize}
            \item signature 1 by B = Sign(B's private key, ``Yes.'')
            \item will check with Verify(B's public key, signature 1 by B, ``Yes.'')
        \end{itemize}
    \item  A$\rightarrow$B: Vegetarian? [signature 2 by A]  \\
     B$\rightarrow$A: No, not this time. [signature 2 by B]  \\ \ldots \\
     A$\rightarrow$B: There's a guy at the door, says he's here to repair the AC. Should I let him in? [signature $N$ by A]
    \vspace{.5cm}
    \item since attacker can't forge signed messages, everything's okay?
    \end{itemize}
\end{frame}

\begin{frame}{replay attacks}
    \begin{itemize}
    \item A$\rightarrow$B: Did you order lunch? [signature 1 by A] \\
          B$\rightarrow$A: Yes. [signature 1 by B]  \\
          A$\rightarrow$B: Vegetarian? [signature 2 by A] \\
          B$\rightarrow$A: No, not this time. [signature 2 by B] \\
          \ldots \\
          A$\rightarrow$B: There's a guy at the door, says he's here to repair the AC. Should I let him in? [signature $N$ by A]
    \vspace{.5cm}
    \item how can attacker hijack the reponse to A's inquiry?
    \item<2-> \myemph<2>{as an attacker, I can copy/paste B's earlier message!}
        \begin{itemize}
        \item just keep the same signature, so it can be verified!
        \item Verify(B's public key, ``Yes.'', signature 2 from B) = 1
        \end{itemize}
    \end{itemize}
\end{frame}


\begin{frame}{nonces}
    \begin{itemize}
    \item one solution to replay attacks:
    \item A$\rightarrow$B: \myemph{\#1} Did you order lunch? [signature 1 from A]
        \begin{itemize}
        \item signature from A = Sign(A's private key, ``\myemph{\#1} Did you order lunch?'')
        \end{itemize}
    \item B$\rightarrow$A: \myemph{\#1} Yes. [signature 1 from B] \\
    A$\rightarrow$B: \myemph{\#2} Vegetarian? [signature 2 from A] \\
    B$\rightarrow$A: \myemph{\#2} No, not this time. [signature 2 from B] \\
    \ldots \\
    A$\rightarrow$B: \myemph{\#54} There's a guy at the door, says he's here to repair the AC. Should I let him in? [signature $N$ from A] \\
    \vspace{.5cm}
    \item (assuming A actually checks the numbers)
    \end{itemize}
\end{frame}

% \begin{frame}{nonces (2)}
%     \begin{itemize}
%     \item another solution to replay attacks:
%     \item B$\rightarrow$A: [next number \myemph{\#91523}] [signature from B] \\
%     A$\rightarrow$B: \myemph{\#91523} Did you order lunch? [next number \myemph{\#90382}] [signature from A] \\
%     B$\rightarrow$A: \myemph{\#90382} Yes. [next number \myemph{\#14578}] [signature from B] \\
%     \ldots \\
%     A$\rightarrow$B: \myemph{\#6824} There's a guy at the door, says he's here to repair the AC. Should I let him in? [next number \myemph{\#36129}][signature from A]
%     \vspace{.5cm}
%     \item (assuming A actually checks the numbers)
%     \end{itemize}
% \end{frame}

\begin{frame}{replay attacks (alt)}
    \begin{itemize}
    \item M$\rightarrow$B: \#54 Did you order lunch? [signature by M] \\
          B$\rightarrow$M: \#54 Yes. [signature intended for M by B]  \\
    \hrule
    \item<2-> A$\rightarrow$B: \#54 There's a guy at the door, says he's here to repair the AC. Should I let him in? [signature $N$ by A]
    \vspace{.5cm}
    \item<2-> how can M hijack the response to A's inquiry?
    \item<3-> \myemph<3>{as an attacker, I can copy/paste B's earlier message!}
        \begin{itemize}
        \item just keep the same signature, so it can be verified!
        \item Verify(B's public key, ``\#54 Yes.'', signature intended for M by B) = 1
        \end{itemize}
    \end{itemize}
\end{frame}

% \begin{frame}{confusion about who's sending?}
%     \begin{itemize}
%     \item in addition to nonces, either
%         \begin{itemize}
%         \item write down more who is sending + other context so message can't be reused and/or
%         \item use unique set of keys for each principal you're talking to
%         \end{itemize}
%     \vspace{.5cm}
%     \item with symmetric encryption, also ``reflection attacks''
%         \begin{itemize}
%         \item A sends message to B, attacker sends A's message back to A as if it's from B
%         \end{itemize}
%     \end{itemize}
% \end{frame}
